\begin{definition}
  \emph{(Affine set and hull)}
  A set 
  $A\subseteq \R^n$
  is called \textbf{affine}, if
  \begin{gather}
    \alpha x + (1-\alpha)y \in A
    \quad
    \text{for all}
    \ 
    x,y \in A
    \ 
    \text{and}
    \ 
    \alpha \in \R.
  \end{gather}
  The \textbf{affine hull} 
  $\mathrm{aff}(\Omega)$
  of a set 
  $\Omega\subseteq \R^n$
  is the smallest affine set that includes $\Omega.$
\end{definition}

\begin{definition}
  \emph{(Relative interior)}
  Let 
  $\Omega\subseteq \R^n.$
  We define the \textbf{relative interior} of $\Omega$ by
  \begin{gather}
    \mathrm{ri}(\Omega)
    :=
    \left\{ 
      x \in \Omega 
      \colon
      \text{there exists}\ 
      \gamma > 0\ 
      \text{such that}\ 
      \mathrm{B}_\gamma(x)
      \cap
      \mathrm{aff}(\Omega)
      \in
      \Omega
    \right\}.
  \end{gather}

\begin{proposition}
  Let $C$ be a non-empty convex set in $\R^n.$ Then we get the representation
  \begin{gather}
    \mathrm{ri}(C)
    =
    \left\{ 
      z \in C
      \colon
      \text{for all}\ 
      x \in C \ 
      \text{there exists}\ 
      t > 0 \ 
      \text{such that}\ 
      z + t (z-x)
      \in C
    \right\}.
  \end{gather}
\end{proposition}
\begin{proof}
  \cite[Theorem~6.4]{Rockafellar1970}
\end{proof}
\begin{proposition}
  Let $C_1\subseteq \R^{n_1}$ and $C_2\subseteq \R^{n_2}$ be two non-empty convex sets. Then it holds
  \begin{gather}
    \mathrm{ri}(C_1\times C_2)
    = 
    \mathrm{ri}(C_1)
    \times
    \mathrm{ri}(C_2).
  \end{gather}
\end{proposition}
\begin{proof}
  Let
  $
  (z_1, z_2)
  \in 
  \mathrm{ri}(C_1\times C_2).
  $
  Then for all 
  $
  (x_1, x_2)
  \in 
  C_1\times C_2
  $
  there exists
  $t>0$
  such that
  \begin{gather}
      z_i + t (z_i-x_i)
      \in C_i
      \qquad
      \text{for}\ 
      i\in \left\{ 1,2 \right\}.
  \end{gather}
  This proves $\subseteq.$
  Suppose 
  $
    z_1 
    \in
    \mathrm{ri}(C_1)
  $
  and
  $
    z_2 
    \in
    \mathrm{ri}(C_2).
  $
  Let
  $
    (x_1,x_2)\in C_1\times C_2
  $
  with corresponding $t_1,t_2 >0$.
  If $t_1=t_2$ everything is clear.
  W.l.o.g.
  assume 
  $t_1<t_2$. Define $\theta:=\frac{t_1}{t_2}\in (0,1).$
  By the convexity of $C_2$ it follows
  \begin{gather}
    z_2 + t_1 (z_2 - x_2)
    =
    \theta
    (
    z_2 + t_2 (z_2 - x_2)
    )
    +
    (1-\theta)z_2
    \in C_2.
  \end{gather}
  Thus
  $
  (z_1,z_2)\in\mathrm{ri}(C_1\times C_2). 
  $
  This proves $\supseteq$ and equality.
\end{proof}
  
\begin{ftheorem}
  \emph{(Convex separation in finite dimension)}
  Let $C_1$ and $C_2$ be two non-empty convex sets in $\R^n$. 
  Then $C_1$ and $C_2$ can be properly separated if and only if 
  $\mathrm{ri}(C_1)\cap\mathrm{ri}(C_2)=\emptyset.$
\end{ftheorem}
\begin{proof}
  \cite[Theorem~11.3]{Rockafellar1970}
\end{proof}
\end{definition}
