In the formulation of Theorem~\ref{dual} we encounter "If (...) there exists the optimal solution $(\rho^\dagger,\lambda_0^\dagger,\lambda)$ ... " .
To be able to study asymptotic properties of the solutions we have to become independent of this assumption.
There are two observations that help with that.
First, if we solve Problem~\ref{dual} on a compact search space, there always exists a measurable solution (if the objective function is Caratheodory).
Second (with hindsight), we want optimal solutions to estimate an oracle parameter $\lambda^*$ well. 
To this end, we will define a compact parameter space that always contains the oracle parameter $\lambda^*$ and restrict Problem~\ref{dual} to it.
Then Theorem~\ref{th:argmax} gives us a measurable solution of the restricted Problem~\ref{dual}.
In some cases, this is only a local solution. It becomes global if it is in the interior of the compact parameter space.
Thus we call it the restricted, or the pseudo solution.

Consider 
the random vector (the oracle parameter)
\begin{align*}
  \lambda^*
  \ 
  :=
  \ 
  \left(
  0_{N},0,
  \left[
  \varphi^{'}
  \left(
  \frac
  {1}
  {\pi(X_i)}
  \right)
\right]_{i\in \left\{
  1,\ldots,N
\right\}}
  \right)
\end{align*}
with values in 
$\R^N_{\ge 0}\times \R\times \R^N$
.
By Assumption~\ref{asu:objective_f} (continuity of $\varphi^{'}$)
and Assumption\ref{asu:ps} ($\pi$ is continuous and bounded away from 0)
there exists (for all $N\in\mathbb{N}$) a compact set 
$
\Theta_N\subset
\R^N_{\ge 0}\times \R\times \R^N
$
that contains $\lambda^*$. 
We employ Theorem~\ref{th:argmax} to show, that there exists a measurable solution to Problem~\ref{dual} restricted to $\Theta_N^1$,
where 
\begin{align*}
  \Theta_N^1
  :=
  \left\{
    x\in 
\R^N_{\ge 0}\times \R\times \R^N
|
\norm{x-y}_2\le 1
\ 
\text{for some}\ 
y\in\Theta_N
  \right\}
  \,.
\end{align*}
\begin{lemma}
  \label{lem:pseud_sol}
  For all $N\in\mathbb{N}$ there exists a (pseudo) solution
  \begin{align*}
    s_N\colon
    \Omega
    \to
  \R^N_{\ge 0}
  \times
  \R
  \times
  \R^{N}
  \end{align*}
  to
  Problem~\ref{dual} restricted to $\Theta_N^1$ 
  that is
$
  \left(
  \mathcal{A},\mathcal{B}
  \left(
  \R^N_{\ge 0}
  \times
  \R
  \times
  \R^{N}
  \right)
  \right)
$-measurable.
If $s_N\in \mathrm{int}\, \Theta_N^1$, then it is the global solution
  $
  (\rho^\dagger,\lambda_0^\dagger,\lambda^\dagger)
  $.
\end{lemma}
\begin{proof}
Consider the (constant) correspondence
\begin{align*}
  \psi
  \colon
  (\Omega,\mathcal{A},\P)
  \ 
  \twoheadrightarrow
  \ 
  \R^N_{\ge 0}
  \times
  \R
  \times
  \R^{N}
  \,,
  \qquad
  \omega
  \ 
  \to
  \ 
  \Theta_N^1
  \,.
\end{align*}
This is weakly measurable, because $\Theta_N^1$ is deterministic.
Indeed,
$\Theta_N^1\cap O\neq\emptyset$ is either true or false, that is,
  \begin{gather*}
    \left\{ 
      \omega\in \Omega
      \ 
      |
      \ 
      \psi(\omega)
      \cap
      O
      \neq
      \emptyset
    \right\}
    \ 
    \in
    \ 
    \left\{ \Omega,\emptyset \right\}
    \subset
    \mathcal{A}
    \qquad
    \text{for all open subsets}
    \ 
    O
    \subset
  \R^N_{\ge 0}
  \times
  \R
  \times
  \R^{N}
    \,.
  \end{gather*}
  Next, consider the (random) objective function of (the maximize version of) Problem~\ref{dual}, that is,
  \begin{align*}
    &
  G\colon
  \Omega
  \times
  \left(
  \R^N_{\ge 0}
  \times
  \R
  \times
  \R^{N}
  \right)
  \to
  \R\cup \left\{
    -\infty
  \right\}
  \intertext{with}
    &
  G(\omega,(\rho,\lambda_0,\lambda))
  \ 
  =
  \ 
  -\infty
  \qquad 
  \text{if}\ 
  \rho_i\neq 0\  \text{for some}\ i>n
  \,,
  \\
  \intertext{and}\qquad
  &
  G(\omega,(\rho,\lambda_0,\lambda))
  \\
  &
  \ 
  =
  \ 
  \frac{1}{N}
\sum_{i=1} 
  ^N
  \Big[
    -
  T_i(\omega)
  \cdot
  \varphi^*
  \!
  \left( 
    \rho_i
    +
\lambda_0
+
\inner
{B(X_i)(\omega)}
{
\lambda
}
  \right)
  \ 
  +
  \ 
\lambda_0
+
\inner
{B(X_i)(\omega)}
{
\lambda
}
\Big]
  \ 
-
\ 
\inner
{\delta(\omega)}
{
  |\lambda|
}
\,.
  \end{align*}
  Clearly, the (random) objective function $G$  is a Caratheodory function. This follows from the (assumed) continuity of $\varphi^*$ and the measurability 
  of all random variables included.
  Since $G$ is also strictly concave, it has a unique argmax $s_N$  in $\Theta_N^1$. 
  By Theorem~\ref{th:argmax} this is $
  \left(
  \mathcal{A},\mathcal{B}
  \left(
  \R^N_{\ge 0}
  \times
  \R
  \times
  \R^{N}
  \right)
  \right)
$-measurable.
Furthermore, by the strict concavity of $G$, if $s_N\in \mathrm{int}\,\Theta_N^1$, then it's the global optimal also global. 
\end{proof}

We will prove later, that with probability going to 1 the latter will be the case.
Furthermore, we will prove, that the (measurable) solution converges to the random variable in probability.
